More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-11 2016-Weak-FH-Bisim/WeakBisim.tex

We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})\!* (\OTarrow{\alpha})(\OTarrow{\tau})* $.

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  \\
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
There exist  sets of $\beta^1_i$, $\beta^2_i$, and $\beta^3_i$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
If only if there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

\end{lemma}

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J_1|\gamma_j\neq\emptyset\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$

@@

\end{corollary}
\begin{proof}
Sketch for discussion.\\

@@

\begin{mathpar}
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
         \implies

 \Bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
 \end{mathpar}
2) From Definition \ref{def-Weak-bisim} we have:

>>>>

We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})^* (\OTarrow{\alpha})(\OTarrow{\tau})^* $.

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

\end{enumerate}
\end{lemma}

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$

@@

\end{corollary}
\begin{proof}
Sketch for discussion.\\
Definition 14 implies definition above

WE SUPPOSE DEF 14, AND 
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

we want
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
with the side conditions ....

@@

\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies

 \Bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
 \end{mathpar}

2) on the alpha we apply def 14: From Definition \ref{def-Weak-bisim} we have:
